---
title: "Academic record"
author: "Pablo Rodríguez-Sánchez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    toc: false
    includes:
      in_header: headers/header_with_date.md
  html_document:
    toc: true
---

```{r Setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
```

```{r Dependencies, warning=FALSE, message=FALSE}
rm(list = ls())

source('auxs.R')

library(knitr)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(readr)
library(sp)
```


```{r Load, warning=FALSE, message=FALSE}
key <- read_file('key.txt')
data <- tryCatch(
  {
    data <- parse_academic_production(key)
  },
  error = function(cond){
    message('Unable to access URL. Using backup version')

    load('./backups/backup.Rda')
    return(data)
  }
  )
```

```{r Backups}
save(data, file='./backups/backup.Rda')
write.csv(data, file='./backups/backup.csv', fileEncoding='UTF-8')
```

```{r FilterFuture}
data <- filter(data, Date < today())
```

```{r Filter, warning=FALSE}
data_table <- select(data, Date, Name, Type, Language)
```

## Secondments
```{r Secondments}
secs <- filter(data, Type == 'Secondment')
secs <- select(secs, Date, End.date, Institution, Country)
secs <- mutate(secs, Duration = round(difftime(End.date, Date, units='weeks')))

secs_duration <- sum(secs$Duration)
```

I've spent `r secs_duration` weeks in secondments, distributed as the following:

```{r SecondmentsTab}
kable(secs, format='markdown')
```

## Conferences and workshops
```{r Conferences}
confs <- filter(data, (Type == 'Congress' | Type == 'Workshop') & (Role == 'Attendant' | Role == 'Organizer' | Role == 'Invited speaker' | Role == 'Poster'))
confs <- select(confs, Date, NameURL, Institution, Role, Country, Language)

confs_num <- nrow(confs)
```

I've attended `r confs_num` congresses and workshops:

```{r ConferencesTab}
kable(confs, format='markdown')
```

## Talks
```{r Talks}
talks <- filter(data, Type != 'Course' & (Role == 'Speaker' | Role == 'Teaching assistant'))
talks <- select(talks, Date, NameURL, Type, Institution, Language)

talks_num <- nrow(talks)
```

I've given `r talks_num` talks:

```{r TalksTab}
kable(talks, format='markdown')
```

## Teaching
```{r Classes}
classes <- filter(data, Type == 'Course' & (Role == 'Teacher' | Role == 'Teaching assistant'))
classes <- select(classes, Date, End.date, Name, Role, Institution, Language)

classes_num <- nrow(classes)
```

I've been involved in the teaching of `r classes_num` courses:

```{r ClassesTab}
kable(classes, format='markdown')
```

## Books and book chapters
```{r Books}
books <- filter(data, Type == 'Book' & (Role == 'Chapter author' | Role == 'Author'))
books <- select(books, Date, Name, Institution, Language)
kable(books, format='markdown')
```

## Science communication activity
```{r Scicomm}
sci_comm <- filter(data, Type == 'Article')
sci_comm_table <- select(sci_comm, Date, NameURL, Institution, Language)

sci_comm_table_en <- filter(sci_comm_table, Language == 'English')
sci_comm_table_en <- select(sci_comm_table_en, -Language)

sci_comm_table_es <- filter(sci_comm_table, Language == 'Spanish')
sci_comm_table_es <- select(sci_comm_table_es, -Language)
```

Up to date, I've published `r nrow(sci_comm)` science communication essays: `r nrow(sci_comm_table_en)` in English, and `r nrow(sci_comm_table_es)` in Spanish.

```{r ScicommDates}
hist(sci_comm$Date, breaks=20)
```

Science communication publications in English:

```{r ScicommEnglish}
kable(sci_comm_table_en, format='markdown')
```

Science communication publications in Spanish:

```{r ScicommTab}
kable(sci_comm_table_es, format='markdown')
```

```{r ScicommDist}
ggp <- ggplot(sci_comm, aes(x=Institution))
ggp <- ggp + geom_bar(fill='red') + ggtitle('Science communication essays')
ggp <- ggp + xlab('Publisher') + ylab('Amount')

ggp
```

## Visited countries

I've visited the following countries for academic reasons:

```{r Map, warning=FALSE, message=FALSE}
map <- plot_map(data$Country)
```

***

Built with R `r getRversion()` and RStudio.
