---
title: "Public dissemination of science"
author: "Pablo Rodríguez-Sánchez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: false
  md_document:
    toc: false
    includes:
      in_header: headers/temp.md
---

```{r Setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
```

```{r Dependencies, warning=FALSE, message=FALSE}
source('auxs.R')
source('config.R')

library(knitr)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(readr)
library(sp)
```


```{r Load, warning=FALSE, message=FALSE}
key <- read_file('key.txt')
data <- get_data(key, save_backup = TRUE, ignore_future = TRUE)
```

```{r Filter, warning=FALSE}
data_table <- select(data, Date, Name, Type, Role, Language)
```

```{r Scicomm}
sci_comm <- filter(data, Type == 'Article')
sci_comm_table <- select(sci_comm, Date, NameURL, Institution, Language)

sci_comm_table_en <- filter(sci_comm_table, Language == 'English')
sci_comm_table_en <- select(sci_comm_table_en, -Language)

sci_comm_table_es <- filter(sci_comm_table, Language == 'Spanish')
sci_comm_table_es <- select(sci_comm_table_es, -Language)
```

```{r Talks}
talks <- filter(data, Type == 'Talk')
talks <- select(talks, Date, NameURL, Institution, Language)
```

```{r Other}
other <- filter(data, Type == 'Interview' | Type == 'Podcast' | Type == 'TV' | Type == 'Radio')
other_table <- select(other, Date, NameURL, Type, Role, Institution, Language)
```

Up to date, I've given `r nrow(talks)` talks for a general audience. Additionally, I've published `r nrow(sci_comm)` science communication blog pieces: `r nrow(sci_comm_table_en)` in English, and `r nrow(sci_comm_table_es)` in Spanish.

### Talks
```{r TalksTab}
kable(talks, format='markdown')
```

### Science communication publications in English

```{r ScicommEnglish}
kable(sci_comm_table_en, format='markdown')
```

### Science communication publications in Spanish

```{r ScicommTab}
kable(sci_comm_table_es, format='markdown')
```

### Others
```{r Others tab}
kable(other_table, format='markdown')
```

```{r ScicommDist, eval=FALSE}
ggp <- ggplot(sci_comm, aes(x=Institution))
ggp <- ggp + geom_bar(fill='red') + ggtitle('Science communication essays')
ggp <- ggp + xlab('Publisher') + ylab('Amount')

ggp
```

***

Built with R `r getRversion()` and RStudio.
